API design for machine learning software: experiences from the scikit-learn project

### 2013-08-05 paper.tex
unnecessary "the"

\citet{pedregosa2011} briefly presented \sklearn and
benchmarked it against several competitors.
In this paper, we instead present an
in-depth analysis of design choices made when building the library,
detailing how we organized and operationalized
common machine learning concepts.
We first present in section~\ref{sec:core-api} the central application
programming interface (API) and then describe, in section~\ref{sec:advanced-api},
advanced API mechanisms built on the core interface.
Section~\ref{sec:implementation} briefly describes the implementation.
Section~\ref{sec:comparison} then
compares \sklearn to other major projects in terms of API\@.
Section~\ref{sec:future_work} outlines some of the objectives for
a \sklearn 1.0 release.
We summarize and conclude in section~\ref{sec:conclusions}.

@@

Estimator initialization and actual learning are strictly separated,
in a way that is similar to partial function application:
an estimator is initialized from a set of named constant hyper-parameter values
(e.g., the $C$ constant in SVMs)
and can be considered as a function
that maps these values to actual learning algorithms.
The constructor of an estimator does not see any actual data, nor does it perform any actual learning.
All it does is attach the given parameters to the object.
For the sake of convenient model inspection, hyper-parameters are set as public attributes,
which is especially important in model selection settings.
For ease of use, default hyper-parameter values are also provided
for all built-in estimators.
These default values are set to be relevant in most common
situations in order to make estimators as effective as possible
\textit{out-of-box} for non-experts.

>>>>

\citet{pedregosa2011} briefly presented \sklearn and
benchmarked it against several competitors.
In this paper, we instead present an
in-depth analysis of design choices made when building the library,
detailing how we organized and operationalized
common machine learning concepts.
We first present in section~\ref{sec:core-api} the central application
programming interface (API) and then describe, in section~\ref{sec:advanced-api},
advanced API mechanisms built on the core interface.
Section~\ref{sec:implementation} briefly describes the implementation.
Section~\ref{sec:comparison} then
compares \sklearn to other major projects in terms of API\@.
Section~\ref{sec:future_work} outlines some of the objectives for
a \sklearn 1.0 release.
We conclude by summarizing the major points of this paper in
section~\ref{sec:conclusions}.

@@

Estimator initialization and actual learning are strictly separated,
in a way that is similar to partial function application:
an estimator is initialized from a set of named constant hyper-parameter values
(e.g., the $C$ constant in SVMs)
and can be considered as a function
that maps these values to actual learning algorithms.
The constructor of an estimator does not see any actual data, nor does it perform any actual learning.
All it does is attach the given parameters to the object.
For the sake of convenient model inspection, hyper-parameters are set as public attributes,
which is especially important in model selection settings.
For ease of use, default hyper-parameter values are also provided
for all built-in estimators.
These default values are set to be relevant in many common
situations in order to make estimators as effective as possible
\textit{out-of-box} for non-experts.
